\documentclass[margin, 12pt]{article} % Use the res.cls style, the font size can be changed to 11pt or 12pt here
\usepackage{palatino}

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\setlength{\textwidth}{5.1in} % Text width of the document

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf Shiori IKAWA} % Your name at the top
 

\moveleft.5\hoffset\centerline{8295 BPO Way, Piscataway} % Your address
\moveleft.5\hoffset\centerline{NJ, USA 08854}
\moveleft.5\hoffset\centerline{(848)-239-9913}
\moveleft.5\hoffset\centerline{shiori.ikawa@rutgers.edu}

\parindent=0pt
%----------------------------------------------------------------------------------------


%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------
 
\section*{EDUCATION}  


2016-Present Ph.D. Student. Linguistics. Rutgers, The State University of New Jersey
\begin{itemize}
\item
Interest: syntax-semantics interface, lexical semantics, Argument Structure, selection, language acquisition

\end{itemize}
2014-2016 M.A., Department of Language and Information Sciences, The University of Tokyo
\begin{itemize}
\item Thesis: Difference in Syntactic Structure between Internally and Externally Caused Change of State Verbs: through an Investigation of Japanese Deverbal Compounds
\end{itemize}


2010-2014 B.A., The University of Tokyo, Department of Language and Information Sciences

\section*{GRANT / FELLOWSHIP / AWARDS}

Fulbright Scholarship, Aug 2016-Present\\

Research Fellowship for Young Scientists (DC1), Japan Society for the Promotion of Science, Apr-Jul 2016\\

Ichikoh Memorial Award (award for outstanding performance), Graduate School of Arts and Sciences, The University of Tokyo, Mar 2016\\

IPA Student Award of International Congress of Phonetic Sciences 2015, International Phonetic Association, Aug 2015\\

Type1 Scholarship, Japan Student Services Organization (with Loan Exemption for Outstanding Academic Achievement), Apr2014-Mar 2016


%----------------------------------------------------------------------------------------
%	Technology SKILLS SECTION
%----------------------------------------------------------------------------------------

\section*{CONFERENCE PAPER} 

Ikawa, S., Takimoto, K., \& Grenon, I. 2015. "Can acoustic cues used in L1 really be used to perceive novel sound contrasts?" In {\sl Proceedings of the XVIII International Congress of Phonetic Sciences}, Glasgow, Scotland.2015 

%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
 
\section*{PRESENTATIONS}

Ikawa, S. {\sl Nihongo-sinki-doosi ni miru muidoo-hennyuu no kahi} [The possibility of conflation: viewed from the novel verbs in Japanese]. Lexicon Study Circle. July, 2017. Tokyo, Japan.\\

Ikawa, S. {\sl Naiteki-sieki-jyootai henka-doosi no koozoo ni tuite} [On the structure of Internally Caused Change of State verbs], the 151st meeting of the Linguistic Society of Japan. November, 2015. Nagoya, Japan. \\

Ikawa, S., Takimoto, K., \& Grenon, I. "Can acoustic cues used in L1 really be used to perceive novel sound contrasts?" in International Congress of Phonetic Sciences. August, 2015. Glasgow, Scotland.\\

Ikawa, S. {\sl Doosi-yurai-hukugoogo no rendaku ni okeru daiichi-yooso no koosei no eikyoo} [The effect of argumenthood of the first element on rendaku in deverbal compounds], Morpohlogy and Lexiocn Forum 2014. Osaka, Japan.



%----------------------------------------------------------------------------------------
%	COMMUNITY SERVICE SECTION
%---------------------------------------------------------------------------------------- 

\section*{TEACHING EXPERIENCE}
Teaching Assistant at Department of Language and Information Sciences, The University of Tokyo
\begin{itemize}
\item Apr 2014-Jul 2016 Japanese Sign Language, Instructor: Fumie Shimojo (Apr 2014-Jan 2016) / Nobue Kobayashi, Takeo Noguchi (Apr 2016-Jul 2016)
\item Oct 2014-Jan 2015 Foundation of Language Sciences 1: Introduction to Linguistics, Instructor: Takane Ito
\item Apr 2014-Jul 2014 Linguistic Theory 1: Introduction to Generative Syntax, Instructor: Tsuneko Nakazawa
\end{itemize}


%----------------------------------------------------------------------------------------
%	EXTRA-CURRICULAR ACTIVITIES SECTION
%----------------------------------------------------------------------------------------

\section*{PROFESSIONAL SERVICES} 
Research Assistant, Center for Evolutionary Cognitive Sciences, The University of Tokyo, May 2016-Jun 2016,\\

Part-time Staff Member, Laboratory for Language Development, RIKEN Brain Science Institute, Jul 2014-Mar 2017

%----------------------------------------------------------------------------------------

\end{document}